Developing a preprint culture in biology

### 2013-02-26 ms.tex
fix compilation issue;
Revising PeerJ box section to include biology focus

PeerJ (\href{https://peerj.com/}{https://peerj.com/}) is a new commercial open
access publisher that combines both a preprint server and a peer reviewed
journal. Preprints can be made private and shared only with selected colleagues.
Only one preprint per year can be posted for free, with a onetime (\emph{i.e.}
lifetime) fee required to allow an author to post unlimited public preprints.
Preprints can be posted to PeerJ regardless of where they will eventually be
submitted for publication.

@@

\begin{table}[!ht]
    \caption{\bf{Popular options for preprints}}}
    \begin{tabular}{|l|cccccccc|}
    \hline
    Website               & Free & Comments & Private preprints & Moderated & Peer-reviewed & DOI & Version-Control & Other Content\\
    \hline
    arXiv.org             & Yes & No & No & Yes & No & No & No & No\\
    figshare.com          & Yes & Yes & No & No & No & Yes & No & Yes\\
    peerj.com             & No & Yes & Yes & No & No & Yes & No & No\\
    f1000research.com     & No & Yes & No & Yes & Yes & Yes & No & No\\
    github.com            & Yes & Yes & Yes & No & No & No & Yes & Yes\\
    \hline
    \end{tabular}
    \label{table:box1}
\end{table}

>>>>

PeerJ (\href{https://peerj.com/}{https://peerj.com/}) is a new commercial open
access publisher that provides a preprint server and a peer reviewed journal. It
is focused on the biological sciences, which may counter the perception that
preprints do not have a place in biology. Preprints can optionally be made
private.  One preprint per year can be posted for free, with a onetime
(\emph{i.e.}  lifetime) fee for unlimited public preprints. Preprints can be
posted to PeerJ regardless of where they will be submitted for publication.

@@

\begin{table}[!ht]
    \caption{\bf{Popular options for preprints}}
    \begin{tabular}{|l|cccccccc|}
    \hline
    Website               & Free & Comments & Private preprints & Moderated & Peer-reviewed & DOI & Version-Control & Other Content\\
    \hline
    arXiv.org             & Yes & No & No & Yes & No & No & No & No\\
    figshare.com          & Yes & Yes & No & No & No & Yes & No & Yes\\
    peerj.com             & No & Yes & Yes & No & No & Yes & No & No\\
    f1000research.com     & No & Yes & No & Yes & Yes & Yes & No & No\\
    github.com            & Yes & Yes & Yes & No & No & No & Yes & Yes\\
    \hline
    \end{tabular}
    \label{table:box1}
\end{table}
